---
title: "More Timely Payment of Property Taxes Through Simplification"
author: "Sloboda - Pavlovský - Sičáková-Beblavá - Szabo"
date: "2025-07-01"
output: html_document
---

```{r setup, echo=FALSE}
knitr::opts_chunk$set(eval = TRUE, 
                      echo = FALSE, 
                      message=FALSE, 
                      warning = FALSE, 
                      kable.caption = NA, 
                      results = "asis")

knitr::opts_knit$set(root.dir = "~/Library/Mobile Documents/com~apple~CloudDocs/Documents/ÚVP - veda, prednášky/veda_Administrative burden/Property tax paper/Submit_EaG")
```

## Read Me

This file replicates the analysis of the following paper: "*More Timely Payment of Property Taxes Through Simplification*". The file replicates the results shown in the main text as well as in the Supplementary Materials.

```{r, message=FALSE}
rm(list = ls())

# Required Libraries 
library(rio)
library(tidyverse)
library(gridExtra)
library(estimatr) # lm_robust 
library(margins)
library(modelsummary) # modelsummary
library(kableExtra)
library(sjPlot)
library(car)
library(marginaleffects)

# Importing Dataset
raw_data <- import("tax_compliance.csv")

# Renaming variable names from Slovak to English 
data <- raw_data %>% 
  dplyr::rename(
    ID = REFERENCNECISLO, 
    Gender = POHLAVIE, 
    Age = VEK,
    Tax_total = DANCELKOM,
    Tax_paid = UHRADENACIASTKA, 
    Tax_paid_before_duedate = UHRADENACIASTKADOSPLATNOSTI,
    Tax_paid_after_duedate = UHRADENACIASTKAPOSPLATNOSTI, 
    Tax_outstanding = ZOSTAVAUHRADIT, 
    Treatment = INTERVENCIA,
    Tax_declaration_21 = PRIZNANIE2021A,
    Admin_ID = CISLOSPRAVKYNE
    ) 

# Recoding Gender Variable 
data <- data %>% 
  mutate(Gender = case_match(Gender, 
    "zena" ~ "F", 
    "muz" ~ "M"
  )) %>% 
  mutate(sex = if_else(Gender == "M", 0, 1)) %>% 
  relocate(sex, .after = Gender)

data$Gender <- factor(data$Gender, levels = c("M", "F"))

# Recoding Treatment Variable 
data <- data %>%  
 mutate(Treatment = case_match(Treatment,
                                "Export DZN A" ~ "A",
                                "Export DZN B" ~ "B",
                                "Export DZN C" ~ "C",
                                "Export DZN D" ~ "D",
                                "Export DZN E" ~ "E")) %>% 
  mutate(Treatment_full = case_match(Treatment,
                                "A" ~ "Control",
                                "B" ~ "Simplification",
                                "C" ~ "Simplification + Social Norm",
                                "D" ~ "Simplification + Deterrence",
                                "E" ~ "Simplification + Public Good Appeal")) %>% 
  relocate(Treatment_full, .after = Treatment)


data$Treatment_full <- factor(data$Treatment_full, levels = c("Control", "Simplification", "Simplification + Social Norm", "Simplification + Deterrence", "Simplification + Public Good Appeal"))

# Setting as Factor 
data <- data %>% 
  mutate(Admin_ID = as.factor(Admin_ID)) %>% 
  mutate(Tax_declaration_21 = as.factor(Tax_declaration_21)) 

# Creating the Outcome Variable(s) Tax_paid_singlepay & Tax_paid_install 
data <- data %>% 
  mutate(Residul_tax_before_duedate = Tax_total - Tax_paid_before_duedate) %>% 
  mutate(Tax_paid_singlepay = if_else(Residul_tax_before_duedate == 0, 1, 0)) %>% 
   mutate(Tax_paid_late = if_else(Tax_paid_after_duedate == 0, 0, 1)) %>% 
   mutate(Tax_paid_install = if_else(Tax_paid_before_duedate == 0, 0, 1))
```

```{r}
# Materials and procedures - Number of Obs. per Each Treatment for Table 1 
obs_per_treatment <- data %>% 
  group_by(Treatment_full) %>% 
  summarise(n = n())

# print(obs_per_treatment)
```

```{r}
## Number of Taxpayers per Administrator and Treatment
admin_check <- data %>% 
  group_by(Admin_ID, Treatment) %>% 
  dplyr::summarise(n = n()) %>% 
  pivot_wider(names_from = Treatment, values_from = n) %>% 
  mutate(across(where(is.integer), ~replace_na(., 0))) %>% 
  relocate(A, .before = B) %>% 
  relocate(D, .before = E)
```

```{r}
# Filtering wrongly assigned treatments (more than one treatment per administrator) 
admin_dominant <- data %>%
  dplyr::count(Admin_ID, Treatment) %>%
  group_by(Admin_ID) %>%
  slice_max(n, n = 1, with_ties = FALSE) %>%
  ungroup() %>%
  dplyr::select(Admin_ID, Treatment)

data_subset <- data %>%
  inner_join(admin_dominant, by = c("Admin_ID", "Treatment"))

# nrow(data) - nrow(data_subset)  

# n_admin <- data_subset %>% 
#  group_by(Admin_ID) %>% 
#  summarise(n = n()) 

# range(n_admin$n)

# data_subset %>% 
#  group_by(Treatment) %>% 
#  summarise(Count = n_distinct(Admin_ID))
```

```{r}
# Descriptive Statistics of the Selected Variable per Each Treatment
treatment_randomization_check <- data_subset %>% 
  group_by(Treatment) %>% 
  dplyr::summarise(
    `Mean tax total` = round(mean(Tax_total), 2), 
    `Mean tax paid` = round(mean(Tax_paid), 2), 
    `Mean tax outstanding` = round(mean(Tax_outstanding), 2), 
    `Share of people filling tax declaration in 2021 (%)` = round(mean(Tax_declaration_21 == "1", na.rm = TRUE) * 100, 2), 
    `Share of female (%)` = round(mean(sex)*100, 2),
    `Mean age` = round(mean(Age), 2)) %>% 
   pivot_longer(
    cols = -Treatment,
    names_to = "Statistics",
    values_to = "Value"
  ) %>% 
  pivot_wider(
    names_from = Treatment,
    values_from = Value
  )

print(treatment_randomization_check)
```

```{r}
# Treatment Randomization Check - Total Tax Burden
# anova1 <- aov(Tax_total ~ Treatment, data = data_subset)
# summary(anova1)
# anova1.residuals <- residuals( object = anova1 )   
# qqnorm(anova1.residuals)
# nortest::ad.test(anova1.residuals)

anova_tax <- kruskal.test(Tax_total ~ Treatment, data = data_subset)

anova_tax_df <- data.frame(
  Statistic = anova_tax$statistic,
  `p value` = anova_tax$p.value,
  df = anova_tax$parameter
)

pairwise_wilcox <- pairwise.wilcox.test(
  data_subset$Tax_total, 
  data_subset$Treatment,
  p.adjust.method = "bonferroni"
)

pairwise_wilcox_df <- as.data.frame(pairwise_wilcox$p.value)%>% 
   mutate(across(where(is.numeric), ~ round(., 3)))

pairwise_wilcox_df <- pairwise_wilcox_df %>%
  mutate(across(where(is.numeric), ~ ifelse(is.na(.), "-", format(round(., 2), nsmall = 2)))) %>%
  mutate(across(everything(), ~ ifelse(. == "1.00", "1.00", .)))

print(anova_tax_df)
print(pairwise_wilcox_df)

## Table B.1d: Treatment Randomization Check - Gender 
# chisq_gender <- CrossTable(data_subset$Gender, data_subset$Treatment, 
#            prop.r = FALSE,
#            prop.c = FALSE,
#            prop.t = FALSE,
#            prop.chisq = FALSE,
#            chisq = TRUE)

Gender_Treatment <- table(data_subset$Gender, data_subset$Treatment)
chisq_df <- chisq.test(Gender_Treatment)

chisq_gender_df <- data.frame(
  Statistic = chisq_df$statistic,
  `p value` = chisq_df$p.value,
  df = chisq_df$parameter
)

print(chisq_gender_df)

## Table B.1e: Treatment Randomization Check - Age
# anova2 <- aov(Age ~ Treatment, data = data_subset)
# summary(anova2)
# anova2.residuals <- residuals(object = anova2)   
# qqnorm(anova2.residuals)
# nortest::ad.test(anova2.residuals)

anova_age <- kruskal.test(Age ~ Treatment, data = data_subset)

anova_age_df <- data.frame(
  Statistic = anova_age$statistic,
  `p value` = anova_age$p.value,
  df = anova_age$parameter
)

pairwise_wilcox_age <- pairwise.wilcox.test(
  data_subset$Age, 
  data_subset$Treatment,
  p.adjust.method = "bonferroni"
)

pairwise_wilcox_age_df <- as.data.frame(pairwise_wilcox_age$p.value)%>% 
   mutate(across(where(is.numeric), ~ round(., 3)))

pairwise_wilcox_age_df <- pairwise_wilcox_age_df %>%
  mutate(across(where(is.numeric), ~ ifelse(is.na(.), "-", format(round(., 2), nsmall = 2)))) %>%
  mutate(across(everything(), ~ ifelse(. == "1.00", "1.00", .)))

print(anova_age_df)
print(pairwise_wilcox_age_df)

## Treatment Randomization Check - Tax Declaration 
Tax_declaration_Treatment <- table(data_subset$Tax_declaration_21, data_subset$Treatment)
chisq_df <- chisq.test(Tax_declaration_Treatment)

chisq_Tax_declaration_df <- data.frame(
  Statistic = chisq_df$statistic,
  `p value` = chisq_df$p.value,
  df = chisq_df$parameter
)

print(chisq_Tax_declaration_df)
```

```{r}
## Share of Taxpayers by Age Decil 
age_mean <- mean(data_subset$Age)

plot_age <- ggplot(data = data_subset, aes(x = Age)) + 
  geom_histogram(fill = "grey", colour = "black", bins = 10)+
  stat_function(fun = function(x) dnorm(x, mean = mean(data$Age), sd = sd(data$Age)),
                color = "black", linetype = "dotted") + 
  geom_vline(xintercept = age_mean, linetype = "dashed", color = "black")+
  theme(
    text = element_text(face = "plain")  
  ) +
  theme_classic() +
  labs(y = "No. of observations", x = "Age") 

print(plot_age)
```

```{r}
# Filtering out age outliers 
data_subset <- data_subset %>% 
  mutate(Age_outlier = if_else(Age < 18 | Age > 100, 1, 0)) 

# data_subset %>% 
#  group_by(Age_outlier) %>% 
#  summarise(n = n())

data_subset <- data_subset %>%
  filter(Age_outlier != 1)
```

```{r}
## Distribution of the Tax-Related Variables  

plot_Tax_total <- ggplot(data = data_subset, aes(x = Tax_total)) + 
  geom_density(fill = "grey")+
  theme_classic()+
  labs(y = "",
       x = "Total tax")

plot_Tax_total_paid <- ggplot(data = data_subset, aes(x = Tax_paid)) + 
  geom_density(fill = "grey")+
  theme_classic()+
  labs(y = "",
       x = "Total tax paid")

plot_Tax_paid_before_duedate  <- ggplot(data = data_subset, aes(x = Tax_paid_before_duedate)) + 
  geom_density(fill = "grey")+
  theme_classic()+
  labs(y = "",
       x = "Tax paid before the due date")
  
plot_Tax_paid_after_duedate  <- ggplot(data = data_subset, aes(x = Tax_paid_after_duedate)) + 
  geom_density(fill = "grey")+
  theme_classic()+
  labs(y = "",
       x = "Tax paid after the due date")

plot_Tax_outstanding  <- ggplot(data = data_subset, aes(x = Tax_outstanding)) + 
  geom_density(fill = "grey")+
  theme_classic()+
  labs(y = "",
       x = "Outstanding tax")

grid.arrange(plot_Tax_total,plot_Tax_total_paid,  plot_Tax_paid_before_duedate, plot_Tax_paid_after_duedate, plot_Tax_outstanding)
```

```{r}
## Descriptives Statistics per Treatment after the Cleaning Process (Table 2)
table2 <- data_subset %>% 
  group_by(Treatment_full) %>% 
  summarise(N = n(),
            `Sex (% Female)` = round(mean(sex)*100,2),
            `Mean Age` = round(mean(Age),2),
            `SD Age` = round(sd(Age), 2),
            `Mean Tax` = round(mean(Tax_total),2),
            `SD Tax` = round(sd(Tax_total), 2),
            `Filling Tax Declaration in 2021 (%)` = round(mean(as.numeric(Tax_declaration_21))*100 - 100, 2))

print(table2)
```

```{r}
## Descriptives Statistics after the Cleaning Process (Appendix B.3)
## Descriptive Statistics of the Numeric Variables (Ungrouped by Treatment) 
desc_stat <- data_subset %>% 
  select(sex, Age, Tax_total, Tax_paid, Tax_paid_before_duedate,
         Tax_paid_after_duedate, Tax_outstanding, Residual_tax_before_duedate,
         Tax_paid_singlepay, Tax_paid_late, Tax_paid_ontime) %>% 
  psych::describe() %>% 
  select(-c(vars, n, trimmed, mad))

rownames(desc_stat) <- c(
  "Gender (Female = 1)", "Age", "Tax total", "Tax paid",
  "Tax paid before duedate", "Tax paid after duedate", "Tax outstanding",
  "Tax residual before duedate", "Tax paid in a single payment",
  "Tax paid late", "Tax paid in a single payment / installments")
print(desc_stat)
```

```{r}
## Distribution of Total Tax Burden Across the Control and Treatment Groups
tax_dist_treat <- data_subset %>%
  ggplot(aes(x = Treatment_full, y = Tax_total, fill = Treatment_full)) +
  geom_violin(alpha = .3, colour = NA) +                       
  geom_boxplot(width = .15, outlier.shape = NA) +              
  stat_summary(geom = "point", fun = "mean", shape = 4, size = 2) +
  scale_y_log10() +                                            
  theme_classic() +
  labs(y = "Tax total (EUR, log scale)", x = "Treatment") +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 30, hjust = 1, size = 8)) +
  scale_fill_grey()
```

## Analysis
### Average Treatment Effects (DV = Tax paid in a Single Payment or Installments)
```{r}
model1 <- lm_robust(Tax_paid_ontime ~ Treatment_full, 
                    data = data_subset, clusters = Admin_ID, se_type = "CR2")

model2 <- lm_robust(Tax_paid_ontime ~ Treatment_full + Tax_total + Tax_declaration_21 + Gender + Age + I(Age^2), data = data_subset, clusters = Admin_ID, se_type = "CR2")

model3 <- lm_robust(Tax_paid_ontime ~ Treatment_full + Tax_total + Tax_declaration_21 + Gender + Age, data = data_subset, clusters = Admin_ID, se_type = "CR2")

model_summary1 <- tidy(model1, conf.int = TRUE)
model_summary1$model <- "Model1"

model_summary2 <- tidy(model2, conf.int = TRUE)
model_summary2$model <- "Model2"

model_summary3 <- tidy(model3, conf.int = TRUE)
model_summary3$model <- "Model3"

model_all <- rbind(model_summary1, model_summary3, model_summary2) 

model_two <- rbind(model_summary1, model_summary3) 

model_all <- model_all %>%
  mutate(
    Treatment = gsub("Treatment_full", "", term)
  ) %>% 
  relocate(Treatment, .after = term) 

model_all <- model_all %>% 
  filter(!grepl("Admin|Age|Gender|Tax", term)) %>% 
  mutate(Treatment = if_else(Treatment == "(Intercept)", "Control", Treatment)) %>% 
  select(-term)

model_two <- model_two %>%
  mutate(
    Treatment = gsub("Treatment_full", "", term)
  ) %>% 
  relocate(Treatment, .after = term) 

model_two <- model_two %>% 
  filter(!grepl("Admin|Age|Gender|Tax", term)) %>% 
  mutate(Treatment = if_else(Treatment == "(Intercept)", "Control", Treatment)) %>% 
  select(-term)

model_all$Treatment <- factor(model_all$Treatment, levels = 
                                c("Simplification + Public Good Appeal",
                                   "Simplification + Deterrence", 
                                   "Simplification + Social Norm", 
                                  "Simplification", 
                                  "Control"
                                  ))

model_two$Treatment <- factor(model_two$Treatment, levels = 
                                c("Simplification + Public Good Appeal",
                                   "Simplification + Deterrence", 
                                   "Simplification + Social Norm", 
                                  "Simplification", 
                                  "Control"
                                  ))

model_all$model <- factor(model_all$model,
  levels = c("Model1", "Model2", "Model3"),
  labels = c("No covariates", "Covariates + Age squared", "Covariates + Age linear"))

model_two$model <- factor(model_two$model,
  levels = c("Model1", "Model3"),
  labels = c("No covariates", "With Covariates"))

figure1 <- model_all %>% 
  filter(!Treatment == "Control") %>% 
  mutate(estimate = estimate*100,
         conf.low = conf.low*100,
         conf.high = conf.high*100) %>% 
  ggplot(aes(y = Treatment, x = estimate, colour = model)) +
  geom_errorbar(aes(xmin = conf.low, xmax = conf.high), width=0, position= position_dodge(width=0.5)) +
   geom_point(aes(x = estimate, shape = model), position = position_dodge(width=0.5), size=2) +
  scale_x_continuous(limits=c(-1, 2.5), breaks = round(seq(-1, 2.5, by = .5), 2))+
  geom_vline(xintercept = 0, linetype = "dashed")+
  labs(x = expression(atop("Predicted Treatment Effect (95% CI)", italic("Property Tax Timely Payment (single payment or instalments)"), 
      )),  y = "") +
  theme_classic() +
  theme(axis.text.y = element_text(angle = 30, hjust = 1, size = 8)) + 
 scale_shape_discrete(name = "Models") +
  scale_colour_grey(name = "Models", start = 0.2, end = 0.8, aesthetics = "colour") +
  theme(legend.position="right") 

figure1_paper <- model_two %>% 
  filter(!Treatment == "Control") %>% 
  mutate(estimate = estimate*100,
         conf.low = conf.low*100,
         conf.high = conf.high*100) %>% 
  ggplot(aes(y = Treatment, x = estimate, colour = model)) +
  geom_errorbar(aes(xmin = conf.low, xmax = conf.high), width=0, position= position_dodge(width=0.5)) +
   geom_point(aes(x = estimate, shape = model), position = position_dodge(width=0.5), size=2) +
  scale_x_continuous(limits=c(-1, 2.5), breaks = round(seq(-1, 2.5, by = .5), 2))+
  geom_vline(xintercept = 0, linetype = "dashed")+
  labs(x = expression(atop("Predicted Treatment Effect (95% CI)", italic("Property Tax Timely Payment (single payment or instalments)"), 
      )),  y = "") +
  theme_classic() +
  theme(axis.text.y = element_text(angle = 30, hjust = 1, size = 8)) + 
 scale_shape_discrete(name = "Models") +
  scale_colour_grey(name = "Models", start = 0.2, end = 0.8, aesthetics = "colour") +
  theme(legend.position="right") 
```

```{r}
## Linear Hypothesis Tests 
lh_social_norm <- linearHypothesis(model2, "Treatment_fullSimplification + Social Norm = Treatment_fullSimplification")
Chisq_social_norm <- round(lh_social_norm$Chisq[2], 4)
Df_social_norm <- lh_social_norm$Res.Df[2]
P_social_norm <- round(lh_social_norm$`Pr(>Chisq)`[2], 4)

lh_deterrence <- linearHypothesis(model2, "Treatment_fullSimplification + Deterrence = Treatment_fullSimplification")
Chisq_deterrence <- round(lh_deterrence$Chisq[2], 4)
Df_deterrence <- lh_deterrence$Res.Df[2]
P_deterrence <- round(lh_deterrence$`Pr(>Chisq)`[2], 4)

lh_public <- linearHypothesis(model2, "Treatment_fullSimplification + Public Good Appeal = Treatment_fullSimplification")
Chisq_public <- round(lh_public$Chisq[2], 4)
Df_public <- lh_public$Res.Df[2]
P_public <- round(lh_public$`Pr(>Chisq)`[2], 4)

# Create a data frame with the results
lh_results <- data.frame(
  Treatment = c(
    "Simplification + Social Norm",
    "Simplification + Deterrence",
    "Simplification + Public Good Appeal"
  ),
  Chisq = c(Chisq_social_norm, Chisq_deterrence, Chisq_public),
  Df = c(Df_social_norm, Df_deterrence, Df_public),
  p_value = c(P_social_norm, P_deterrence, P_public)
)

print(lh_results)
```

```{r}
## Predicted Probability of Tax Compliance across the Control and Treatment Groups (95% CI)
pred_model_1 <- avg_predictions(model1, by = "Treatment_full")
pred_model_2 <- avg_predictions(model2, by = "Treatment_full")
pred_model_3 <- avg_predictions(model3, by = "Treatment_full")

pred_model_1$model <- "Model 1: no covariates"
pred_model_2$model <- "Model 2: covariates + Age + Age^2"
pred_model_3$model <- "Model 3: covariates + Age"

preds_all <- bind_rows(as.data.frame(pred_model_1),
                       as.data.frame(pred_model_3),
                       as.data.frame(pred_model_2))
preds_two <- bind_rows(as.data.frame(pred_model_1),
                       as.data.frame(pred_model_3))

preds_two$Treatment_full <- factor(preds_two$Treatment_full,
  levels = c("Control", "Simplification", "Simplification + Social Norm",
             "Simplification + Deterrence", "Simplification + Public Good Appeal"))

plot_pred_prob <- ggplot(preds_two, aes(Treatment_full, estimate, colour = model)) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high),
                width = 0, position = position_dodge(width = 0.5)) +
  geom_point(aes(shape = model), position = position_dodge(width = 0.5), size = 2) +
  coord_cartesian(ylim = c(.92, .95)) +    
  ylab("Predicted Probability of Tax Compliance (95% CI)") +
  xlab("") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1, size = 8)) +
  scale_shape_discrete(name = "Models",
                       labels = c("No covariates", "Covariates")) +
  scale_colour_grey(name = "Models",
                    labels = c("No covariates", "Covariates"),
                    start = 0.2, end = 0.8) +
  theme(legend.position = "right")
```

```{r Regression table, include=FALSE}
cm <- c(
  "Treatment_fullSimplification"                      = "Simplification",
  "Treatment_fullSimplification + Social Norm"        = "Simplification + Social Norm",
  "Treatment_fullSimplification + Deterrence"         = "Simplification + Deterrence",
  "Treatment_fullSimplification + Public Good Appeal" = "Simplification + Public Good Appeal",
  "Tax_total"           = "Tax total",
  "Tax_declaration_211" = "Tax declaration 2021",  # term name assumes level "1"
  "GenderF"             = "Female",
  "Age"                 = "Age",
  "I(Age^2)"            = "Age squared"
)

modelsummary(
  list("Simple model" = model1, "Model with Age linear" = model3,
       "Model with Age squared" = model2),
  statistic = "std.error",
  stars     = c('***' = .001, '**' = .01, '*' = .05),
  coef_map  = cm,
  gof_map   = c("nobs", "r.squared", "adj.r.squared"),
  notes     = "Cluster-robust (CR2) standard errors, clustered at the administrator level (31 clusters), in parentheses."
)

```{r}
### Heterogeneous Treatment Effects (DV = Tax paid on-time in full or in part)
#### Heterogeneous Treatment Effects - Gender
model_HTE_gender <- lm_robust(Tax_paid_ontime ~ Treatment_full * Gender + Tax_total + Tax_declaration_21 + Age, data = data_subset, clusters = Admin_ID, se_type = "CR2")

hte_gender <- avg_comparisons(
  model_HTE_gender,
  variables = "Treatment_full",
  by        = "Gender"
) %>%
  mutate(
    Treatment = gsub(" - Control$", "", contrast),
    Gender    = case_when(Gender == "F" ~ "Female",
                          Gender == "M" ~ "Male",
                          TRUE ~ as.character(Gender))
  )

treatment_order <- c("Simplification + Public Good Appeal",
                     "Simplification + Deterrence",
                     "Simplification + Social Norm",
                     "Simplification")

plot_inter_gender <- hte_gender %>%
  mutate(estimate  = estimate  * 100,
         conf.low  = conf.low  * 100,
         conf.high = conf.high * 100,
         Treatment = factor(Treatment, levels = treatment_order)) %>%
  ggplot(aes(y = Treatment, colour = Gender)) +
  geom_errorbar(aes(xmin = conf.low, xmax = conf.high),
                width = 0, position = position_dodge(width = 0.5)) +
  geom_point(aes(x = estimate, shape = Gender),
             position = position_dodge(width = 0.5), size = 2) +
  geom_vline(xintercept = 0, colour = "grey", linetype = "dashed") +
  scale_x_continuous(breaks = round(seq(-1, 3, by = .5), 2)) +
  coord_cartesian(xlim = c(-1, 3)) +
  scale_colour_grey("Gender") +
  scale_shape_discrete("Gender") +
  theme_classic() +
  theme(axis.text.y = element_text(angle = 30, hjust = 1, size = 8),
        plot.title  = element_text(hjust = 0.5, face = "bold")) +
  labs(
    x = expression(atop("Predicted Treatment Effect (95% CI)",
                        italic("Property Tax Payment (single payment or instalments)"))),
    y = ""
  )
```

```{r}
hte_gender_diff <- tidy(model_HTE_gender) %>%
  filter(grepl(":GenderF$", term)) %>%
  select(term, estimate, std.error, statistic, df, p.value, conf.low, conf.high) %>%
  mutate(p_holm = p.adjust(p.value, method = "holm"))

lh_results <- hte_gender_diff %>%
  mutate(Treatment = gsub("Treatment_full|:GenderF", "", term)) %>%
  select(Treatment, estimate, std.error, statistic, df, p.value, p_holm)
```


```{r}
## Figure C.1b: Predicted Probability of Tax Compliance across Treatment Groups and Gender
plot_int_gender <- plot_model(model_HTE_gender, 
           type = "pred",
           terms = c("Treatment_full[all]", "Gender[all]"),
           #colors = "bw",
           legend.title = "Gender")+
  theme_classic() + 
  labs(y = "Predicted Probability of Tax Compliance (95% CI)", title = "", x = "")+ 
  scale_colour_grey(labels = c("Male", "Female"))
```

```{r}
## Heterogeneous Treatment Effects by Age  
model_HTE_age <- lm_robust(Tax_paid_ontime ~ Treatment_full * Age + Treatment_full * I(Age^2) + Tax_total + Tax_declaration_21 + Gender, data = data_subset, clusters = Admin_ID, se_type = "CR2")

plot1_age <- plot_model(model_HTE_age, 
           type = "pred",
           terms = c("Age[all]", "Treatment_full[Control, Simplification]"),
           colors = "bw",
           legend.title = "Treatment type")+
  theme_classic() + 
  labs(y = "Predicted Probability of Tax Compliance (95% CI)", title = "")+
  theme(legend.position = "bottom")

plot2_age <- plot_model(model_HTE_age, 
           type = "pred",
           terms = c("Age[all]", "Treatment_full[Control, Simplification + Social Norm]"),
           colors = "bw",
           legend.title = "Treatment type")+
  theme_classic() + 
  labs(y = "Predicted Probability of Tax Compliance (95% CI)", title = "")+
  theme(legend.position = "bottom")

plot3_age <- plot_model(model_HTE_age, 
           type = "pred",
           terms = c("Age[all]", "Treatment_full[Control, Simplification + Deterrence]"),
           colors = "bw",
           legend.title = "Treatment type")+
  theme_classic() + 
  labs(y = "Predicted Probability of Tax Compliance (95% CI)", title = "")+
  theme(legend.position = "bottom")

plot4_age <- plot_model(model_HTE_age, 
           type = "pred",
           terms = c("Age[all]", "Treatment_full[Control, Simplification + Public Good Appeal]"),
           colors = "bw",
           legend.title = "Treatment type")+
  theme_classic() + 
  labs(y = "Predicted Probability of Tax Compliance (95% CI)", title = "")+
  theme(legend.position = "bottom")

age_seq <- seq(min(data_subset$Age, na.rm = TRUE),
               max(data_subset$Age, na.rm = TRUE), by = 1)

hte_age <- comparisons(
  model_HTE_age,
  variables = "Treatment_full",
  newdata   = datagrid(Age = age_seq)
) %>%
  mutate(
    Treatment = gsub(" - Control$", "", contrast),
    Treatment = factor(Treatment, levels = c(
      "Simplification", "Simplification + Social Norm",
      "Simplification + Deterrence", "Simplification + Public Good Appeal"))
  )

plot_inter_age_cont <- hte_age %>%
  mutate(estimate  = estimate  * 100,
         conf.low  = conf.low  * 100,
         conf.high = conf.high * 100) %>%
  ggplot(aes(x = Age, y = estimate)) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.2, fill = "dimgrey") +
  geom_line(size = .8, colour = "dimgrey") +
  geom_hline(yintercept = 0, colour = "darkgrey", linetype = "dashed") +
  facet_wrap(~ Treatment) +
  coord_cartesian(xlim = c(20, 100)) +
  theme_classic() +
  labs(x = "Age",
       y = expression(atop("Predicted Treatment Effect (95% CI)",
                          italic("Property Tax Timely Payment (single payment or instalments)")))) +
  theme(legend.position = "none")

```

```{r}
## Figure C1c: Heterogeneous Treatment Effects by Age (linear)
model_HTE_age_linear <- lm_robust(Tax_paid_ontime ~ Treatment_full * Age + I(Age^2) + Tax_total + Tax_declaration_21 + Gender, data = data_subset, clusters = Admin_ID, se_type = "CR2")

age_seq <- seq(min(data_subset$Age, na.rm = TRUE),
               max(data_subset$Age, na.rm = TRUE), by = 1)

hte_age_linear <- comparisons(
  model_HTE_age,
  variables = "Treatment_full",
  newdata   = datagrid(Age = age_seq)
) %>%
  mutate(
    Treatment = gsub(" - Control$", "", contrast),
    Treatment = factor(Treatment, levels = c(
      "Simplification", "Simplification + Social Norm",
      "Simplification + Deterrence", "Simplification + Public Good Appeal"))
  )

plot_inter_age_cont_linear <- hte_age_linear %>%
  mutate(estimate  = estimate  * 100,
         conf.low  = conf.low  * 100,
         conf.high = conf.high * 100) %>%
  ggplot(aes(x = Age, y = estimate)) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.2, fill = "dimgrey") +
  geom_line(size = .8, colour = "dimgrey") +
  geom_hline(yintercept = 0, colour = "darkgrey", linetype = "dashed") +
  facet_wrap(~ Treatment) +
  coord_cartesian(xlim = c(20, 100)) +
  theme_classic() +
  labs(x = "Age",
       y = expression(atop("Predicted Treatment Effect (95% CI)",
                          italic("Property Tax Timely Payment (single payment or instalments)")))) +
  theme(legend.position = "none")
```

```{r}
## Predicted Tax Compliance by Treatment, Age and Gender  
model_HTE_gender_age <- lm_robust(Tax_paid_ontime ~ Treatment_full * Gender * Age + Treatment_full * Gender * I(Age^2) + Tax_total + Tax_declaration_21, data = data_subset, clusters = Admin_ID, se_type = "CR2")

plot_gender_age <- plot_predictions(
  model_HTE_gender_age,
  condition = list(
    Age            = 20:100,
    Gender        = unique,
    Treatment_full = c("Simplification", "Simplification + Social Norm",
                       "Simplification + Deterrence", "Simplification + Public Good Appeal")
  )) +
  theme_classic() +
  coord_cartesian(xlim = c(20, 100)) +
  labs(y = "Predicted Probability of Tax Compliance (95% CI)", title = "", colour = "Gender")

gender_gap <- comparisons(
  model_HTE_gender_age, variables = "Gender",
  newdata = datagrid(Age = c(30, 40, 50, 60, 70, 80),
                     Treatment_full = c("Simplification", "Simplification + Social Norm",
                                        "Simplification + Deterrence",
                                        "Simplification + Public Good Appeal"))
)
gender_gap$p_holm <- p.adjust(gender_gap$p.value, method = "holm")
```

```{r}
## Heterogeneous Treatment Effects by Tax Burden 
tax_cut <- quantile(data_subset$Tax_total, c(.25, .50, .75), na.rm = TRUE)

data_subset <- data_subset %>%
  mutate(Tax_quartile = factor(
    case_when(Tax_total <= tax_cut[1] ~ "Q1",
              Tax_total <= tax_cut[2] ~ "Q2",
              Tax_total <= tax_cut[3] ~ "Q3",
              TRUE                    ~ "Q4"),
    levels = c("Q1", "Q2", "Q3", "Q4")))

values_quartiles <- data_subset %>%
  group_by(Tax_quartile) %>%
  summarise(min_value = min(Tax_total, na.rm = TRUE),
            max_value = max(Tax_total, na.rm = TRUE))

model_HTE_tax <- lm_robust(Tax_paid_ontime ~ Treatment_full * Tax_quartile + Tax_declaration_21 + Gender + Age, data = data_subset, clusters = Admin_ID, se_type = "CR2")

plot_int_tax <- plot_predictions(
  model_HTE_tax,
  condition = c("Treatment_full", "Tax_quartile")
) +
  theme_classic() +
  labs(y = "Predicted Probability of Tax Compliance (95% CI)", title = "", x = "")+ 
  scale_colour_grey(labels = c("Q1 (3 - 35 EUR)",
                               "Q2 (36 - 63 EUR)",
                               "Q3 (64 - 100 EUR)",
                               "Q4 (>101 EUR)")) +
  theme(legend.position = "bottom")

hte_tax <- avg_comparisons(model_HTE_tax, variables = "Treatment_full",
                           by = "Tax_quartile") %>%
  mutate(Treatment = factor(gsub(" - Control$", "", contrast), levels = treatment_order))

plot_inter_tax <- hte_tax %>%
  mutate(across(c(estimate, conf.low, conf.high), ~ . * 100)) %>%
  ggplot(aes(y = Treatment, colour = Tax_quartile)) +
  geom_errorbar(aes(xmin = conf.low, xmax = conf.high),
                width = 0, position = position_dodge(width = 0.5)) +
  geom_point(aes(x = estimate, shape = Tax_quartile),
             position = position_dodge(width = 0.5), size = 2) +
  geom_vline(xintercept = 0, colour = "grey", linetype = "dashed") +
  scale_x_continuous(breaks = round(seq(-1, 4, by = .5), 2)) +
  coord_cartesian(xlim = c(-1, 4)) +
  scale_colour_grey("Tax burden (quartile)") +
  scale_shape_discrete("Tax burden (quartile)") +
  labs(x = expression(atop("Predicted Treatment Effect (95% CI)",
       italic("Property Tax Timely Payment (single payment or instalments)"))),
       y = "") +
  theme_classic() +
  theme(axis.text.y = element_text(angle = 30, hjust = 1, size = 8))
```

```{r}
## Figure C.1f: Predicted Probability of Tax Compliance across Treatment Groups and Tax Quartile  
plot_int_tax <- plot_predictions(
            model_HTE_tax,
           condition = c("Treatment_full", "Tax_quartile"),
           legend.title = "Tax Quartile")+
  theme_classic() + 
  labs(y = "Predicted Probability of Tax Compliance (95% CI)", title = "", x = "")+ 
  scale_colour_grey(labels = c("Q1 (3 - 35 EUR)",
                               "Q2 (36 - 63 EUR)",
                               "Q3 (64 - 100 EUR)",
                               "Q4 (>101 EUR)"))+
  theme(legend.position = "bottom")
```

```{r}
## Heterogeneous Treatment Effects by Tax Declaration  
model_HTE_tax_decl <- lm_robust(Tax_paid_ontime ~ Treatment_full * Tax_declaration_21 + Tax_total + Gender + Age, data = data_subset, clusters = Admin_ID, se_type = "CR2")

hte_tax_decl <- avg_comparisons(model_HTE_tax_decl, variables = "Treatment_full", by = "Tax_declaration_21") %>%
  mutate(
    Treatment = factor(gsub(" - Control$", "", contrast), levels = treatment_order),
    Tax_declaration_2021 = dplyr::recode(Tax_declaration_21,
      "0" = "not filed in 2021", "1" = "filed in 2021")
    )

plot_inter_tax_decl <- hte_tax_decl %>% 
  mutate(estimate = estimate*100, conf.low = conf.low*100, conf.high = conf.high*100) %>%
  ggplot(aes(y = Treatment, colour = Tax_declaration_2021)) +
  geom_errorbar(aes(xmin = conf.low, xmax = conf.high),
                width = 0, position = position_dodge(width = 0.5)) +
  geom_point(aes(x = estimate, shape = Tax_declaration_2021),
             position = position_dodge(width = 0.5), size = 2) +
  geom_vline(xintercept = 0, colour = "grey", linetype = "dashed") +
  scale_x_continuous(breaks = round(seq(-1.5, 4, by = .5), 2)) +
  coord_cartesian(xlim = c(-1.5, 4)) +
  scale_colour_grey("Tax declaration") +
  scale_shape_discrete("Tax declaration") +
  theme_classic() +
  theme(axis.text.y = element_text(angle = 30, hjust = 1, size = 8)) +
  labs(x = expression(atop("Predicted Treatment Effect (95% CI)",
                          italic("Property Tax Timely Payment (single payment or instalments)"))),
       y = "")
```

```{r}
## Predicted Probability of Tax Compliance across Treatment Groups and Tax Declaration 
plot_int_tax_decl <- plot_predictions(
  model_HTE_tax_decl,
  condition = c("Treatment_full", "Tax_declaration_21")
) +
  theme_classic() +
  scale_colour_grey("Tax declaration",
                    breaks = c("0", "1"), labels = c("not filed in 2021", "filed in 2021")) +
  labs(y = "Predicted Probability of Tax Compliance (95% CI)", title = "", x = "")
```

```{r}
### Average Treatment Effects (DV = Tax paid on-time in a single payment)
# Basic Model
model1_singlep <- lm_robust(Tax_paid_singlepay ~ Treatment_full, 
                    data = data_subset, clusters = Admin_ID, se_type = "CR2")

# Model with covariates and age squared
model2_singlep <- lm_robust(Tax_paid_singlepay ~ Treatment_full + Tax_total + Tax_declaration_21 + Gender + Age + I(Age^2), data = data_subset, clusters = Admin_ID, se_type = "CR2")

# Model with covariates and age linear
model3_singlep <- lm_robust(Tax_paid_singlepay ~ Treatment_full + Tax_total + Tax_declaration_21 + Gender + Age, data = data_subset, clusters = Admin_ID, se_type = "CR2")

model_summary1_SP <- tidy(model1_singlep, conf.int = TRUE)
model_summary1_SP$model <- "Model1"

model_summary2_SP <- tidy(model2_singlep, conf.int = TRUE)
model_summary2_SP$model <- "Model2"

model_summary3_SP <- tidy(model3_singlep, conf.int = TRUE)
model_summary3_SP$model <- "Model3"

model_all_SP <- rbind(model_summary1_SP, model_summary2_SP, model_summary3_SP) 

model_two_SP <- rbind(model_summary1_SP, model_summary3_SP) 

model_all_SP <- model_all_SP %>%
  mutate(
    Treatment = gsub("Treatment_full", "", term)
  ) %>% 
  relocate(Treatment, .after = term) 

model_two_SP <- model_two_SP %>%
  mutate(
    Treatment = gsub("Treatment_full", "", term)
  ) %>% 
  relocate(Treatment, .after = term) 

model_all_SP <- model_all_SP %>% 
  filter(!grepl("Admin|Age|Gender|Tax", term)) %>% 
  mutate(Treatment = if_else(Treatment == "(Intercept)", "Control", Treatment)) %>% 
  select(-term)

model_two_SP <- model_two_SP %>% 
  filter(!grepl("Admin|Age|Gender|Tax", term)) %>% 
  mutate(Treatment = if_else(Treatment == "(Intercept)", "Control", Treatment)) %>% 
  select(-term)

model_all_SP$Treatment <- factor(model_all_SP$Treatment, levels = 
                                c("Simplification + Public Good Appeal",
                                   "Simplification + Deterrence", 
                                   "Simplification + Social Norm", 
                                  "Simplification", 
                                  "Control"
                                  ))

model_two_SP$Treatment <- factor(model_two_SP$Treatment, levels = 
                                c("Simplification + Public Good Appeal",
                                   "Simplification + Deterrence", 
                                   "Simplification + Social Norm", 
                                  "Simplification", 
                                  "Control"
                                  ))

model_all_SP$model <- factor(model_all_SP$model,
  levels = c("Model1", "Model2", "Model3"),
  labels = c("No covariates", "Covariates + Age squared", "Covariates + Age linear"))

# Figure with all three models
figure1_SP <- model_all_SP %>% 
  filter(!Treatment == "Control") %>% 
  mutate(estimate = estimate*100,
         conf.low = conf.low*100,
         conf.high = conf.high*100) %>% 
  ggplot(aes(y = Treatment, x = estimate, colour = model)) +
  geom_errorbar(aes(xmin = conf.low, xmax = conf.high), width=0, position= position_dodge(width=0.5)) +
   geom_point(aes(x = estimate, shape = model), position = position_dodge(width=0.5), size=2) +
  scale_x_continuous(limits=c(-1, 3.5), breaks = round(seq(-1, 3.5, by = .5), 2))+
  geom_vline(xintercept = 0, linetype = "dashed")+
  labs(x = expression(atop("Predicted Treatment Effect (95% CI)", italic("Property Tax Timely Payment (single payment or instalments)"), 
      )),  y = "") +
  theme_classic() +
  theme(axis.text.y = element_text(angle = 30, hjust = 1, size = 8)) + 
 scale_shape_discrete(name = "Models") +
  scale_colour_grey(name = "Models", start = 0.2, end = 0.8, aesthetics = "colour") +
  theme(legend.position="right")
```

```{r}
lh_social_norm_SP <- linearHypothesis(model3_singlep, "Treatment_fullSimplification + Social Norm = Treatment_fullSimplification")
Chisq_social_norm_SP <- round(lh_social_norm_SP$Chisq[2], 4)
Df_social_norm_SP <- lh_social_norm_SP$Res.Df[2]
P_social_norm_SP <- round(lh_social_norm_SP$`Pr(>Chisq)`[2], 4)

lh_deterrence_SP <- linearHypothesis(model3_singlep, "Treatment_fullSimplification + Deterrence = Treatment_fullSimplification")
Chisq_deterrence_SP <- round(lh_deterrence_SP$Chisq[2], 4)
Df_deterrence_SP <- lh_deterrence_SP$Res.Df[2]
P_deterrence_SP <- round(lh_deterrence_SP$`Pr(>Chisq)`[2], 4)

lh_public_SP <- linearHypothesis(model3_singlep, "Treatment_fullSimplification + Public Good Appeal = Treatment_fullSimplification")
Chisq_public_SP <- round(lh_public_SP$Chisq[2], 4)
Df_public_SP <- lh_public_SP$Res.Df[2]
P_public_SP <- round(lh_public_SP$`Pr(>Chisq)`[2], 4)

# Create a data frame with the results
lh_results_SP <- data.frame(
  Treatment = c(
    "Simplification + Social Norm",
    "Simplification + Deterrence",
    "Simplification + Public Good Appeal"
  ),
  Chisq = c(Chisq_social_norm_SP, Chisq_deterrence_SP, Chisq_public_SP),
  Df = c(Df_social_norm_SP, Df_deterrence_SP, Df_public_SP),
  p_value = c(P_social_norm_SP, P_deterrence_SP, P_public_SP)
)

```

```{r}
## Predicted Probability of Tax Compliance across the Control and Treatment Groups (95% CI)
pred_model_1_SE <- avg_predictions(model1_singlep, by = "Treatment_full")
pred_model_2_SE <- avg_predictions(model2_singlep, by = "Treatment_full")
pred_model_3_SE <- avg_predictions(model3_singlep, by = "Treatment_full")

pred_model_1_SE$model <- "Model 1: no covariates"
pred_model_2_SE$model <- "Model 2: covariates + Age + Age^2"
pred_model_3_SE$model <- "Model 3: covariates + Age"

preds_two_SE <- bind_rows(as.data.frame(pred_model_1_SE),
                       as.data.frame(pred_model_3_SE))

preds_two_SE$Treatment_full <- factor(preds_two_SE$Treatment_full,
  levels = c("Control", "Simplification", "Simplification + Social Norm",
             "Simplification + Deterrence", "Simplification + Public Good Appeal"))

plot_pred_prob <- ggplot(preds_two_SE, aes(Treatment_full, estimate, colour = model)) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high),
                width = 0, position = position_dodge(width = 0.5)) +
  geom_point(aes(shape = model), position = position_dodge(width = 0.5), size = 2) +
  coord_cartesian(ylim = c(.92, .95)) +    
  ylab("Predicted Probability of Tax Compliance (95% CI)") +
  xlab("") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1, size = 8)) +
  scale_shape_discrete(name = "Models",
                       labels = c("No covariates", "Covariates")) +
  scale_colour_grey(name = "Models",
                    labels = c("No covariates", "Covariates"),
                    start = 0.2, end = 0.8) +
  theme(legend.position = "right")
```

```{r}
## Heterogeneous Treatment Effects by Gender  
model_HTE_gender_SP <- lm_robust(Tax_paid_singlepay ~ Treatment_full * Gender + Tax_total + Tax_declaration_21 + Age, data = data_subset, clusters = Admin_ID, se_type = "CR2")

hte_gender_SP <- avg_comparisons(
  model_HTE_gender_SP,
  variables = "Treatment_full",
  by        = "Gender"
) %>%
  mutate(
    Treatment = gsub(" - Control$", "", contrast),
    Gender    = case_when(Gender == "F" ~ "Female",
                          Gender == "M" ~ "Male",
                          TRUE ~ as.character(Gender))
  )

treatment_order <- c("Simplification + Public Good Appeal",
                     "Simplification + Deterrence",
                     "Simplification + Social Norm",
                     "Simplification")

plot_inter_gender_SP <- hte_gender_SP %>%
  mutate(estimate  = estimate  * 100,
         conf.low  = conf.low  * 100,
         conf.high = conf.high * 100,
         Treatment = factor(Treatment, levels = treatment_order)) %>%
  ggplot(aes(y = Treatment, colour = Gender)) +
  geom_errorbar(aes(xmin = conf.low, xmax = conf.high),
                width = 0, position = position_dodge(width = 0.5)) +
  geom_point(aes(x = estimate, shape = Gender),
             position = position_dodge(width = 0.5), size = 2) +
  geom_vline(xintercept = 0, colour = "grey", linetype = "dashed") +
  scale_x_continuous(breaks = round(seq(-1, 3, by = .5), 2)) +
  coord_cartesian(xlim = c(-1, 3)) +
  scale_colour_grey("Gender") +
  scale_shape_discrete("Gender") +
  theme_classic() +
  theme(axis.text.y = element_text(angle = 30, hjust = 1, size = 8),
        plot.title  = element_text(hjust = 0.5, face = "bold")) +
  labs(
    x = expression(atop("Predicted Treatment Effect (95% CI)",
                        italic("Property Tax Payment (single payment only)"))),
    y = ""
  )
```

```{r}
## Predicted Probability of Tax Compliance across Treatment Groups and Gender
plot_int_gender_SP <- plot_model(model_HTE_gender_SP, 
           type = "pred",
           terms = c("Treatment_full[all]", "Gender[all]"),
           #colors = "bw",
           legend.title = "Gender")+
  theme_classic() + 
  labs(y = "Predicted Probability of Tax Compliance (95% CI)", title = "", x = "")+ 
  scale_colour_grey(labels = c("Male", "Female"))
```

```{r}
## Heterogeneous Treatment Effects by Age 
model_HTE_age_SE <- lm_robust(Tax_paid_singlepay ~ Treatment_full * Age + Treatment_full * I(Age^2) + Tax_total + Tax_declaration_21 + Gender, data = data_subset, clusters = Admin_ID, se_type = "CR2")

hte_age_SE <- comparisons(
  model_HTE_age_SE,
  variables = "Treatment_full",
  newdata   = datagrid(Age = age_seq)
) %>%
  mutate(
    Treatment = gsub(" - Control$", "", contrast),
    Treatment = factor(Treatment, levels = c(
      "Simplification", "Simplification + Social Norm",
      "Simplification + Deterrence", "Simplification + Public Good Appeal"))
  )

## Plot: conf.low // conf.high directly, percentage points
plot_inter_age_cont_SE <- hte_age_SE %>%
  mutate(estimate  = estimate  * 100,
         conf.low  = conf.low  * 100,
         conf.high = conf.high * 100) %>%
  ggplot(aes(x = Age, y = estimate)) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.2, fill = "dimgrey") +
  geom_line(linewidth = .8, colour = "dimgrey") +
  geom_hline(yintercept = 0, colour = "darkgrey", linetype = "dashed") +
  facet_wrap(~ Treatment) +
  coord_cartesian(xlim = c(20, 100)) +
  theme_classic() +
  labs(x = "Age",
       y = expression(atop("Predicted Treatment Effect (95% CI)",
                          italic("Property Tax Timely Payment (single payment only)")))) +
  theme(legend.position = "none")
```

```{r}
## Predicted Probability of Tax Compliance across Treatment Groups and Age
plot1_age_SE <- plot_model(model_HTE_age_SE, 
           type = "pred",
           terms = c("Age[all]", "Treatment_full[Control, Simplification]"),
           colors = "bw",
           legend.title = "Treatment type")+
  theme_classic() + 
  labs(y = "Predicted Probability of Tax Compliance (95% CI) - Single Payment", title = "")+
  theme(legend.position = "bottom")

plot2_age_SE <- plot_model(model_HTE_age_SE, 
           type = "pred",
           terms = c("Age[all]", "Treatment_full[Control, Simplification + Social Norm]"),
           colors = "bw",
           legend.title = "Treatment type")+
  theme_classic() + 
  labs(y = "Predicted Probability of Tax Compliance (95% CI) - Single Payment", title = "")+
  theme(legend.position = "bottom")

plot3_age_SE <- plot_model(model_HTE_age_SE, 
           type = "pred",
           terms = c("Age[all]", "Treatment_full[Control, Simplification + Deterrence]"),
           colors = "bw",
           legend.title = "Treatment type")+
  theme_classic() + 
  labs(y = "Predicted Probability of Tax Compliance (95% CI) - Single Payment", title = "")+
  theme(legend.position = "bottom")

plot4_age_SE <- plot_model(model_HTE_age_SE, 
           type = "pred",
           terms = c("Age[all]", "Treatment_full[Control, Simplification + Public Good Appeal]"),
           colors = "bw",
           legend.title = "Treatment type")+
  theme_classic() + 
  labs(y = "Predicted Probability of Tax Compliance (95% CI) - Single Payment", title = "")+
  theme(legend.position = "bottom")

grid.arrange(plot1_age_full, plot2_age_full, plot3_age_full, plot4_age_full)
```

```{r}
## Predicted Tax Compliance by Treatment, Age and Gender  
model_HTE_gender_age_SE <- lm_robust(Tax_paid_singlepay ~ Treatment_full * Gender * Age + Treatment_full * Gender * I(Age^2) + Tax_total + Tax_declaration_21, data = data_subset, clusters = Admin_ID, se_type = "CR2")

plot_gender_age_SE <- plot_predictions(
  model_HTE_gender_age_SE,
  condition = list(
    Age            = 20:100,
    Gender        = unique,
    Treatment_full = c("Simplification", "Simplification + Social Norm",
                       "Simplification + Deterrence", "Simplification + Public Good Appeal")
  )) +
  theme_classic() +
  coord_cartesian(xlim = c(20, 100)) +
  labs(y = "Predicted Probability of Tax Compliance (95% CI)", title = "", colour = "Gender")

gender_age_gap_SE <- comparisons(
  model_HTE_gender_age_SE,
  variables = "Gender",                                   
  newdata   = datagrid(Age = c(30, 40, 50, 60, 70, 80),
                       Treatment_full = c("Simplification",
                                          "Simplification + Social Norm",
                                          "Simplification + Deterrence",
                                          "Simplification + Public Good Appeal"))
)
```

#### Heterogeneous Treatment Effects - Overall Tax Burden

```{r}
## Heterogeneous Treatment Effects by Tax Burden Single Payment
# use tax_cut object
# use values_quartiles object
# use Tax_quartile variable
# use treatment_order

model_HTE_tax_SE <- lm_robust(Tax_paid_singlepay ~ Treatment_full * Tax_quartile + Tax_declaration_21 + Gender + Age, data = data_subset, clusters = Admin_ID, se_type = "CR2")

hte_tax_SE <- avg_comparisons(
  model_HTE_tax_SE, variables = "Treatment_full", by = "Tax_quartile"
) %>%
  mutate(
    Treatment = factor(gsub(" - Control$", "", contrast), levels = treatment_order))

plot_inter_tax_SE <- hte_tax_SE %>%
  mutate(estimate = estimate*100, conf.low = conf.low*100, conf.high = conf.high*100) %>%
  ggplot(aes(y = Treatment, colour = Tax_quartile)) +
  geom_errorbar(aes(xmin = conf.low, xmax = conf.high),
                width = 0, position = position_dodge(width = 0.5)) +
  geom_point(aes(x = estimate, shape = Tax_quartile),
             position = position_dodge(width = 0.5), size = 2) +
  geom_vline(xintercept = 0, colour = "grey", linetype = "dashed") +
  scale_x_continuous(breaks = round(seq(-1, 4, by = .5), 2)) +
  coord_cartesian(xlim = c(-1, 4)) +
  scale_colour_grey("Tax burden (quartile)") +
  scale_shape_discrete("Tax burden (quartile)") +
  theme_classic() +
  theme(axis.text.y = element_text(angle = 30, hjust = 1, size = 8)) +
  labs(x = expression(atop("Predicted Treatment Effect (95% CI)",
                          italic("Property Tax Timely Payment (single payment only)"))),
       y = "")
```

```{r}
## Predicted Probability of Tax Compliance across Treatment Groups and Tax Quartiles 
plot_int_tax_SE <- plot_predictions(
  model_HTE_tax_SE,
  condition = c("Treatment_full", "Tax_quartile")
) +
  theme_classic() +
  labs(y = "Predicted Probability of Tax Compliance (95% CI) - Single Payment", title = "", x = "")+ 
  scale_colour_grey(labels = c("Q1 (3 - 35 EUR)",
                               "Q2 (35 - 63 EUR)",
                               "Q3 (63 - 100 EUR)",
                               "Q4 (>101 EUR)")) +
  theme(legend.position = "bottom")
```


```{r}
#### Heterogeneous Treatment Effects - Tax Declaration 
model_HTE_tax_decl_SE <- lm_robust(Tax_paid_singlepay ~ Treatment_full * Tax_declaration_21 + Tax_total + Gender + Age, data = data_subset, clusters = Admin_ID, se_type = "CR2")

hte_tax_decl_SE <- avg_comparisons(model_HTE_tax_decl_SE, variables = "Treatment_full", by = "Tax_declaration_21") %>%
  mutate(
    Treatment = factor(gsub(" - Control$", "", contrast), levels = treatment_order),
    Tax_declaration_2021 = dplyr::recode(Tax_declaration_21,
      "0" = "not filed in 2021", "1" = "filed in 2021")
    )

plot_inter_tax_decl_SE <- hte_tax_decl_SE %>% 
  mutate(estimate = estimate*100, conf.low = conf.low*100, conf.high = conf.high*100) %>%
  ggplot(aes(y = Treatment, colour = Tax_declaration_2021)) +
  geom_errorbar(aes(xmin = conf.low, xmax = conf.high),
                width = 0, position = position_dodge(width = 0.5)) +
  geom_point(aes(x = estimate, shape = Tax_declaration_2021),
             position = position_dodge(width = 0.5), size = 2) +
  geom_vline(xintercept = 0, colour = "grey", linetype = "dashed") +
  scale_x_continuous(breaks = round(seq(-1.5, 4, by = .5), 2)) +
  coord_cartesian(xlim = c(-2.5, 4)) +
  scale_colour_grey("Tax declaration") +
  scale_shape_discrete("Tax declaration") +
  theme_classic() +
  theme(axis.text.y = element_text(angle = 30, hjust = 1, size = 8)) +
  labs(x = expression(atop("Predicted Treatment Effect (95% CI)",
                          italic("Property Tax Timely Payment (single payment only)"))),
       y = "")
```

```{r}
## Predicted Probability of Tax Compliance across Treatment Groups and Tax Declaration  
plot_int_tax_decl_SE <- plot_predictions(
  model_HTE_tax_decl_SE,
  condition = c("Treatment_full", "Tax_declaration_21")
) +
  theme_classic() +
  scale_colour_grey("Tax declaration",
                    breaks = c("0", "1"), labels = c("not filed in 2021", "filed in 2021")) +
  labs(y = "Predicted Probability of Tax Compliance (95% CI) - Single Payment", title = "", x = "")
```

```{r}
## Table C.3b: Full Regression Table for Figure C.2a
modelsummary(models = list("Model 1" = model1_full, "Model 2" = model2_full),
                           statistic = "std.error",
                           stars = c('***' = .001, '**' = .01, '*' = .05),
                           coef_omit = c(10), 
                           coef_rename = c("Control", 
                                        "Simplification", 
                                        "Simplification + Social Norm", 
                                        "Simplification + Deterrence", 
                                        "Simplification + Public Good Appeal",
                                        "Tax total", 
                                        "Tax declaration 2021",
                                        "Female", 
                                        "Age"),
                           output = "kableExtra") %>% 
    kable_styling(full_width = FALSE, font_size = 10, latex_options = "HOLD_position")
```

### Figure C.4a:** Treatment Effects Relative to the Control Group (Different Heteroskedasticity-Consistent Covariance Matrix estimators)
```{r}
## Figure C.4a:** Treatment Effects Relative to the Control Group (Different Heteroskedasticity-Consistent Covariance Matrix estimators)

# Model with covariates and standard SE (Non-robust)
model_classic <- lm_robust(Tax_paid_ontime_full_or_part ~ Treatment_full + Tax_total + Tax_declaration_21 + Gender + Age + I(Age^2), data = data_subset_filtered, se_type = "classical")

# Model with covariates and robust SE (HC0)
model_HC0 <- lm_robust(Tax_paid_ontime_full_or_part ~ Treatment_full + Tax_total + Tax_declaration_21 + Gender + Age + I(Age^2), data = data_subset_filtered, se_type = "HC0")

# Model with covariates and robust SE (HC1 - Stata)
model_HC1 <- lm_robust(Tax_paid_ontime_full_or_part ~ Treatment_full + Tax_total + Tax_declaration_21 + Gender + Age + I(Age^2), data = data_subset_filtered, se_type = "HC1")

# Model with covariates and robust SE (HC2)
model_HC2 <- lm_robust(Tax_paid_ontime_full_or_part ~ Treatment_full + Tax_total + Tax_declaration_21 + Gender + Age + I(Age^2), data = data_subset_filtered, se_type = "HC2")

# Model with covariates and robust SE (HC3)
model_HC3 <- lm_robust(Tax_paid_ontime_full_or_part ~ Treatment_full + Tax_total + Tax_declaration_21 + Gender + Age + I(Age^2), data = data_subset_filtered, se_type = "HC3")

model_summary_classic <- tidy(model_classic, conf.int = TRUE)
model_summary_classic$model <- "Classic"

model_summary_HC0 <- tidy(model_HC0, conf.int = TRUE)
model_summary_HC0$model <- "HC0"

model_summary_HC1 <- tidy(model_HC1, conf.int = TRUE)
model_summary_HC1$model <- "HC1"

model_summary_HC2 <- tidy(model_HC2, conf.int = TRUE)
model_summary_HC2$model <- "HC2"

model_summary_HC3 <- tidy(model_HC3, conf.int = TRUE)
model_summary_HC3$model <- "HC3"


model_all_full <- rbind(model_summary_classic, model_summary_HC0, model_summary_HC1, model_summary_HC2, model_summary_HC3) 

model_all_full <- model_all_full %>%
  mutate(
    Treatment = gsub("Treatment_full", "", term)
  ) %>% 
  relocate(Treatment, .after = term) 

model_all_full <- model_all_full %>% 
  filter(!grepl("Age|Gender|Tax", term)) %>% 
  mutate(Treatment = if_else(Treatment == "(Intercept)", "Control", Treatment)) %>% 
  select(-term)

model_all_full$Treatment <- factor(model_all_full$Treatment, levels = 
                                c("Simplification + Public Good Appeal",
                                   "Simplification + Deterrence", 
                                   "Simplification + Social Norm", 
                                  "Simplification", 
                                  "Control"
                                  ))

plot_SE_robust <- model_all_full %>% 
  filter(!Treatment == "Control") %>% 
  mutate(estimate = estimate*100,
         conf.low = conf.low*100,
         conf.high = conf.high*100) %>% 
  ggplot(aes(y = Treatment, x = estimate, colour = model)) +
  geom_errorbar(aes(xmin = conf.low, xmax = conf.high), width=0, position= position_dodge(width=0.5)) +
   geom_point(aes(x = estimate, shape = model), position = position_dodge(width=0.5), size=2) +
  scale_x_continuous(limits=c(-1, 4), breaks = round(seq(-1, 4, by = .5), 2))+
  geom_vline(xintercept = 0, linetype = "dashed")+
  labs(x = "Predicted Treatment Effect (95% CI)", y = "") +
  theme_classic() +
  theme(axis.text.y = element_text(angle = 30, hjust = 1, size = 8)) + 
 scale_shape_discrete(name = "Models", labels = c("Non-robust SE", "HC0 estimator", "HC1 - Stata estimator", "HC2 estimator", "HC3 estimator")) +
  scale_colour_grey(name = "Models", labels = c("Non-robust SE", "HC0 estimator", "HC1 - Stata estimator", "HC2 estimator", "HC3 estimator"), start = 0.2, end = 0.8, aesthetics = "colour") +
  theme(legend.position="right") 
```

```{r Outlier removal sensitity analysis any payment}
# using data_subset_tax

# Basic Model with robust SE
model1b <- lm_robust(Tax_paid_ontime ~ Treatment_full, 
                    data = data_subset_tax, clusters = Admin_ID, se_type = "CR2")

# Age linear
model2b <- lm_robust(Tax_paid_ontime ~ Treatment_full + Tax_total + Tax_declaration_21 + Gender + Age, data = data_subset_tax, clusters = Admin_ID, se_type = "CR2")

model_summary1b <- tidy(model1b, conf.int = TRUE)
model_summary1b$model <- "Model1"

model_summary2b <- tidy(model2b, conf.int = TRUE)
model_summary2b$model <- "Model2"

model_two_b <- rbind(model_summary1b, model_summary2b) 

model_two_b <- model_two_b %>%
  mutate(
    Treatment = gsub("Treatment_full", "", term)
  ) %>% 
  relocate(Treatment, .after = term) 

model_two_b <- model_two_b %>% 
  filter(!grepl("Admin|Age|Gender|Tax", term)) %>% 
  mutate(Treatment = if_else(Treatment == "(Intercept)", "Control", Treatment)) %>% 
  select(-term)

model_two_b$Treatment <- factor(model_two_b$Treatment, levels = 
                                c("Simplification + Public Good Appeal",
                                   "Simplification + Deterrence", 
                                   "Simplification + Social Norm", 
                                  "Simplification", 
                                  "Control"
                                  ))

# regression table
# use cm object
# Reported in the Appendix with three models (with age squared, with age numeric variable, and without age)

modelsummary(
  list("Simple model" = model1b, "Model with Age linear" = model2b),
  statistic = "std.error",
  stars     = c('***' = .001, '**' = .01, '*' = .05),
  coef_map  = cm,
  gof_map   = c("nobs", "r.squared", "adj.r.squared"),
  notes     = "Cluster-robust (CR2) standard errors, clustered at the administrator level (31 clusters), in parentheses.",
  output    = "kableExtra"
) %>%
  kable_styling(full_width = FALSE, font_size = 10, latex_options = "HOLD_position")
```

```{r fig.width=10, fig.height=8}
print(figure1b)
```

```{r Outlier removal sensitivty analysis single payment}
# Basic Model with robust SE
model1b_SP <- lm_robust(Tax_paid_singlepay ~ Treatment_full, 
                    data = data_subset_tax, clusters = Admin_ID, se_type = "CR2")

# Age linear
model2b_SP <- lm_robust(Tax_paid_singlepay ~ Treatment_full + Tax_total + Tax_declaration_21 + Gender + Age, data = data_subset_tax, clusters = Admin_ID, se_type = "CR2")

model_summary1b_SP <- tidy(model1b_SP, conf.int = TRUE)
model_summary1b_SP$model <- "Model1"

model_summary2b_SP <- tidy(model2b_SP, conf.int = TRUE)
model_summary2b_SP$model <- "Model2"

model_two_b_SP <- rbind(model_summary1b_SP, model_summary2b_SP) 

model_two_b_SP <- model_two_b_SP %>%
  mutate(
    Treatment = gsub("Treatment_full", "", term)
  ) %>% 
  relocate(Treatment, .after = term) 

model_two_b_SP <- model_two_b_SP %>% 
  filter(!grepl("Admin|Age|Gender|Tax", term)) %>% 
  mutate(Treatment = if_else(Treatment == "(Intercept)", "Control", Treatment)) %>% 
  select(-term)

model_two_b_SP$Treatment <- factor(model_two_b_SP$Treatment, levels = 
                                c("Simplification + Public Good Appeal",
                                   "Simplification + Deterrence", 
                                   "Simplification + Social Norm", 
                                  "Simplification", 
                                  "Control"
                                  ))

# regression table
# use cm object
# Reported in the Appendix with three models (with age squared, with age numeric variable, and without age)

modelsummary(
  list("Simple model" = model1b_SP, "Model with Age linear" = model2b_SP),
  statistic = "std.error",
  stars     = c('***' = .001, '**' = .01, '*' = .05),
  coef_map  = cm,
  gof_map   = c("nobs", "r.squared", "adj.r.squared"),
  notes     = "Cluster-robust (CR2) standard errors, clustered at the administrator level (31 clusters), in parentheses.",
  output    = "kableExtra"
) %>%
  kable_styling(full_width = FALSE, font_size = 10, latex_options = "HOLD_position")
```

```{r}
saveRDS(list(model1 = model1,
             model2 = model2,
             model3 = model3,
             model1_hc3 = model1_hc3,
             model2_hc3 = model2_hc3,
             model3_hc3 = model3_hc3,
             model_HTE_gender   = model_HTE_gender,
             model_HTE_age      = model_HTE_age,
             model_HTE_age_linear = model_HTE_age_linear,
             model_HTE_gender_age = model_HTE_gender_age,
             model_HTE_tax      = model_HTE_tax,
             model_HTE_tax_decl = model_HTE_tax_decl,
             model1_singlep = model1_singlep,
             model2_singlep = model2_singlep,
             model3_singlep = model2_singlep,
             model_HTE_gender_SP = model_HTE_gender_SP,
             model_HTE_age_SP = model_HTE_age_SP,
             model_HTE_age_linear_SP = model_HTE_age_linear_SP,
             model_HTE_gender_age_SP = model_HTE_gender_age_SP,
             model_HTE_tax_SP      = model_HTE_tax_SP,
             model_HTE_tax_decl_SP = model_HTE_tax_decl_SP
             ),
        "fitted_models.rds")
```